\section{TODOS}
\begin{itemize}
    \item Superblock sometimes does not get marked as unset (but marked as free)
    \item Add "how to use" to this document
    \item Add a "high space usage" mode limiting writes 
    \item Give GC the possibility to officially reset Area to emtpy and unset
    \item Add possibility to having multiple PageAddressCaches
    \item Add possibility to concurrently have same Files open
    \item Add check if dirty in commit Area Summaries to enable read-only (half functioning)
    \item Add userdata write-back upon corrected Biterror
    \item Read validation and error handling. If error is found, either repair it automatically or delay it until scrubbing? Scrubbing would be not very frequent, so on-the-fly would be appreciated.
	\item When ASCache runs full, some used pages cant be marked as dirty. Build sanity checker, scanning whole FS and marking unreachable pages as such.
	\item Implement dynamic number of uncommitted areas to superpage. (Maybe call it Checkpoint?)
	%\item CRC and ECC. How will a broken FS be transferred into a safe state?
	\item Merge DATA and INDEX areas to a single DATA type. Benefits: Less complexity, more efficient space usage, GC desperate mode for unmounting only. But maybe too overdone.
	\item TreeCache - full commit from time to time. (Maybe 'used' marker?)
	\item GC: Static Wear levelling, keep deletioncount in mind.
	\item Implement additional driver function for copying pages for optimizing.
	\item Replace mallocs to variable sized arrays. (Or standard container, b/c variable sized arrays are not legal in c++)
	\item Use Inode pointer space for very small files to speed up access and save space.
	\item Implement DATA Buffer to speed up everything. Note: Low priority and high effort.
\end{itemize}
